Search for Spatially Extended \fermi-LAT Sources Using Two Years of Data

### 2012-04-25 extended_catalog/paper/extended_search.tex
update

\clearpage
\begin{figure}
    \ifcolorfigure
    \plotone{mc_plots/ts_comparison_w44sim_color.eps}
    \else
    \plotone{mc_plots/ts_comparison_w44sim_bw.eps}
    \fi
    % this plot came from $w44simplots/plot_ts_values.py
    \caption{
    \newtext{The distribution of \ts values when fitting statistically
    independent simulations of the
    elliptical ring shaped SNR W44. (a) is the distribution of \ts values
    when fitting W44 as a point-like source and (b) is the
    distribution of \tsext when fitting the SNR with a Gaussian and uniform disk 
    spatial model. (c) is the distribution of the change in TS when
    fitting the source with an elliptical disk spatial model compared to
    fitting it with a radially symmetric spatial model and (d) 
    when fitting the source with a elliptical ring spatial model compared
    to an elliptical disk spatial model.
    }
    }\label{ts_comparison_w44sim}
\end{figure}

\clearpage
\begin{figure}
    \ifcolorfigure
    \plotone{mc_plots/bias_w44sim_color.eps}
    \else
    \plotone{mc_plots/bias_w44sim_bw.eps}
    \fi
    % this plot came from $w44simplots/plot_bias
    \caption{
    \newtext{the distribution of fit parameters
    for the simulation of Monte Carlo simulations of W44.
    The plots show the distribution of (a)
    (a) best fit flux (b) spectral index (c) 68\% containment
    radius (d) eccentricity (e) elliptical orientation angle
    (f) inner ring fraction.
    }
    }\label{bias_w44sim}
\end{figure}

@@

\tablecomments{
\newtext{
For each of the new extended sources, we list any catalog
source that was included in 2FGL to account for residuals induced
by not modeling the extension of a nearby source.
These sources were removed from our model of the sky when studying
the extended source.
}
}
\end{deluxetable}

>>>>

\clearpage
\begin{figure}
    \ifcolorfigure
    \plotone{mc_plots/ts_comparison_w44sim_color.eps}
    \else
    \plotone{mc_plots/ts_comparison_w44sim_bw.eps}
    \fi
    % this plot came from $w44simplots/plot_ts_values.py
    \caption{
    \newtext{The distribution of \ts values when fitting statistically
    independent simulations of W44. (a) is the distribution of \ts values
    when fitting W44 as a point-like source and (b) is the
    distribution of \tsext when fitting the source with a Gaussian and uniform disk 
    spatial model. (c) is the distribution of the change in TS when
    fitting the source with an elliptical disk spatial model compared to
    fitting it with a radially-symmetric disk spatial model and (d) 
    when fitting the source with a elliptical ring spatial model compared
    to an elliptical disk spatial model.
    }
    }\label{ts_comparison_w44sim}
\end{figure}

\clearpage
\begin{figure}
    \ifcolorfigure
    \plotone{mc_plots/bias_w44sim_color.eps}
    \else
    \plotone{mc_plots/bias_w44sim_bw.eps}
    \fi
    % this plot came from $w44simplots/plot_bias
    \caption{
    \newtext{the distribution of fit parameters
    for the simulation of Monte Carlo simulations of W44.
    The plots show the distribution of 
    (a) best fit flux (b) spectral index (c) 68\% containment
    radius (d) eccentricity (e) elliptical orientation angle
    (f) inner ring fraction.
    }
    }\label{bias_w44sim}
\end{figure}

@@

\tablecomments{
\newtext{
For each new extended sources, we list nearby catalog
sources that were included in 2FGL to account for residuals induced
by not modeling the extension of the nearby extended source.
}
}
\end{deluxetable}
